STAT 672: Homework 4

### 2018-04-02 hw4/hw4.tex
kernel space notes

Table 2 depicts the five largest and five smallest weights obtained with
$C=10^{4.5}$. We can interpret these weights. Emails that TALK IN ALL CAPS and
mention money (U.S. dollars) are especially likely to be categorized as spam.
Emails in which the sender mentions the name of someone that we presumably both
know (George) and refers to meeting
(presumably in-person) are indicative of a ``real'' relationship and hence 
are especially likely to be categorized as not-spam.

>>>>

Table 2 depicts the five largest and five smallest weights obtained with
$C=10^{4.5}$. We can interpret these weights. Emails that TALK IN ALL CAPS and
mention money (U.S. dollars) are especially likely to be categorized as spam.
Emails that mention a person that both parties presumably know (George) and that
refer to meeting
(presumably in-person) are indicative of a ``real'' relationship and hence 
are especially likely to be categorized as not-spam.
